Data Specialization for a Staged Lambda Calculus

### 2015-02-25 paper/splitting.tex
various symbol changes

We resolve this mismatch by introducing a translation, called {\em masking} and written $[\xi;v] \vsplito \mathcal{V}$,
which converts residual tables and partial values---like the those above---into a syntactically separated version $\mathcal{V}$.
As before, we enforce the ``syntactically separated'' property structurally,
saying that $\mathcal{V}$ must have the form $\mval i q$ (called a {\em masked value}) where 
$i$ is a monostage value representing the first-stage part of $v$,
and $q$ is a monostage term representing all of the second-stage computation in $\xi$ and $v$.
Note that masking is a technical device for the purpose of stating correctness of splitting at \bbonem; 
it is not part of the splitting algorithm itself.

>>>>

We resolve this mismatch by introducing a translation, called {\em masking} and written $\rtab \xi v \vsplito \mathcal{V}$,
which converts residual tables and partial values---like the those above---into a syntactically separated version $\mathcal{V}$.
As before, we enforce the ``syntactically separated'' property structurally,
saying that $\mathcal{V}$ must have the form $\mval i q$ (called a {\em masked value}) where 
$i$ is a monostage value representing the first-stage part of $v$,
and $q$ is a monostage term representing all of the second-stage computation in $\xi$ and $v$.
Note that masking is a technical device for the purpose of stating correctness of splitting at \bbonem; 
it is not part of the splitting algorithm itself.
